Probabilities of polar alignment in circumbinary disks

### 2024-12-19 src/tex/ms.tex
Talk about effect of j on tp

Note that $\Gamma_1$ depends on $e_\text{b}$, and so it is only a constant in the case of a test particle. For $j>0$, we must compute the precession timescale ourselves. The time coordinate used in Section \ref{sec:rk} is $\tau \equiv \alpha' t$. $\alpha'$ is defined by \citet[see eq. 3.9]{farago2010}, and we write it as
\begin{equation}
    \alpha' \equiv \frac{3}{4} \Omega_\text{b} \left(\frac{a_\text{b}}{r}\right)^{7/2} f(1-f) \,\Gamma_2(j,f,a_\text{b}/a_\text{r}, e_\text{b}) \, ,
\end{equation}
where we have written the $\sqrt{1+m_\text{r}/M_\text{b}}$ factor as $\Gamma_2$. Written in terms of our variables, this expression is very complicated, and we choose to compute it numerically for simplicity. Note, however, that except for extremely large $j$ (e.g. $>10$), $\Gamma_2 \sim 1$.

@@

Figure \ref{fig:t_p} shows that $j$ has two different effects on $t_\text{p}$. The most obvious is that when $j$ changes, the location of the boundary between dynamical regimes also changes. This can cause huge spikes in the timescale ratio as that boundary moves close to the initial conditions $(i_0, \Omega_0)$. The other effect is that the timescale ratio becomes small as $j$ increases.\TJ{I am fairly sure this can be explained by showing that the Kozai-Lidov timescale is proportional to $1/j$, but I have not found a good enough reference yet.}

>>>>

Note that $\Gamma_1$ depends on $e_\text{b}$, and so it is only a constant in the case of a test particle. For $j>0$, we must compute the precession timescale ourselves. The time coordinate used in Section \ref{sec:rk} is $\tau \equiv \alpha' t$. $\alpha'$ is defined by \citet[see eq. 3.9]{farago2010}, and we write it as
\begin{equation}
    \alpha' \equiv \frac{3}{4} \Omega_\text{b} \left(\frac{a_\text{b}}{r}\right)^{7/2} f(1-f) \,\Gamma_2(j,f,a_\text{b}/r, e_\text{b}) \, ,
\end{equation}
where we have written the $\sqrt{1+m_\text{r}/M_\text{b}}$ factor as $\Gamma_2$. Written in terms of our variables, this expression is very complicated, and we choose to compute it numerically for simplicity. Note, however, that except for extremely large $j$ (e.g. $>10$), $\Gamma_2 \sim 1$.

@@

Figure \ref{fig:t_p} shows that $j$ has two different effects on $t_\text{p}$. The most obvious is that when $j$ changes, the location of the boundary between dynamical regimes also changes. This can cause huge spikes in the timescale ratio as that boundary moves close to the initial conditions $(i_0, \Omega_0)$. The other effect is that the timescale ratio becomes small as $j$ increases. We find that the slope for large j is rather consistent, with $t_\text{p}\propto j^{-1} \text{ to } j^{-1.2}$, with the exponent varying slightly with changes to $f$ or $a_\text{b}/r$.
